Flatiron analysis

### 2021-09-16 Rmd/Report 2021.Rmd
Fix bug

  mutate(RDI_grp = case_when(
    relative_dose_intensity < 0.85          ~ "RDI < 0.85",
    relative_dose_intensity >= 0.85         ~ "RDI >= 0.85"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("RDI >= 0.85", "RDI < 0.85"))) %>% 
  mutate(RDI_grp1 = case_when(
    relative_dose_intensity < 0.85          ~ "RDI < 0.85",
    relative_dose_intensity >= 0.85         ~ "RDI >= 0.85",
    relative_dose_intensity >= 0.85         ~ "0.85 <= RDI < 1",
    relative_dose_intensity >= 0.85         ~ "1 <= RDI < 1.5",
    relative_dose_intensity >= 0.85         ~ "1.5 <= RDI < 2",
    relative_dose_intensity >= 0.85         ~ "RDI >= 2",
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("0.85 >= RDI < 1", "0 < RDI < 0.75", "0.75 <= RDI < 0.85", "1 <= RDI < 1.5", 
                                     "1.5 <= RDI < 2", "RDI >= 2"))) %>% 
  # mutate(delay_incare_dx_to_treat = case_when(
  #   str_detect(therapy, "Chemo")     ~ (interval(start = diagnosisdate, end = episodedate)/
  #     duration(n=1, units = "days")),
  #   str_detect(therapy, "Surgery")   ~ (interval(start = diagnosisdate, end = surgerydate)/
  #     duration(n=1, units = "days"))
  # )) %>% 
  # group_by(patientid) %>% 
  # mutate(first_treatment_date = case_when(
  #   treatment_sequence == "Chemotherapy only"             ~ min(episodedate),
  #   str_detect(treatment_sequence, "neo")                 ~ min(episodedate),
  #   treatment_sequence == "surg + adj"                    ~ surgerydate,
  #   treatment_sequence == "Surgery only"                  ~ surgerydate
  # )) %>% 
  # group_by(patientid) %>% 
  # mutate(first_treatment_date = case_when(
  #   str_detect(therapy, "Chemo")                      ~ min(episodedate),
  #   str_detect(therapy, "Surgery")                    ~ surgerydate,
  # )) %>% 
  # mutate(delay_incare_dx_to_treat = interval(start = diagnosisdate, end = first_treatment_date)/
  #                                         duration(n=1, units = "days")) %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  ungroup()

@@

```{r Table 3}
# tbl1 <- 
  analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude != "1") %>% 
  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           had_neo, had_adj,
           "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
#   filter(exclude != "1") %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

>>>>

  mutate(RDI_grp = case_when(
    relative_dose_intensity < 0.85          ~ "RDI < 0.85",
    relative_dose_intensity >= 0.85         ~ "RDI >= 0.85"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("RDI >= 0.85", "RDI < 0.85"))) %>% 
  mutate(RDI_grp1 = case_when(
    relative_dose_intensity < 0.85          ~ "RDI < 0.85",
    # relative_dose_intensity >= 0.85         ~ "RDI >= 0.85",
    relative_dose_intensity >= 0.85 &
      relative_dose_intensity <= 1          ~ "0.85 <= RDI <= 1",
    relative_dose_intensity > 1 &
      relative_dose_intensity <= 1.5        ~ "1 < RDI <= 1.5",
    relative_dose_intensity > 1.5 &
      relative_dose_intensity <= 2          ~ "1.5 < RDI <= 2",
    relative_dose_intensity > 2             ~ "RDI > 2",
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("RDI < 0.85", 
                                     "0.85 >= RDI <= 1", 
                                     "1 < RDI <= 1.5", 
                                     "1.5 < RDI <= 2", 
                                     "RDI > 2"))) %>% 
  # mutate(delay_incare_dx_to_treat = case_when(
  #   str_detect(therapy, "Chemo")     ~ (interval(start = diagnosisdate, end = episodedate)/
  #     duration(n=1, units = "days")),
  #   str_detect(therapy, "Surgery")   ~ (interval(start = diagnosisdate, end = surgerydate)/
  #     duration(n=1, units = "days"))
  # )) %>% 
  left_join(., Treatment) %>% 
  group_by(patientid) %>%
  mutate(first_treatment_date = case_when(
    treatment_sequence == "Chemotherapy only"             ~ min(episodedate),
    str_detect(treatment_sequence, "neo")                 ~ min(episodedate),
    treatment_sequence == "surg + adj"                    ~ surgerydate,
    treatment_sequence == "Surgery only"                  ~ surgerydate
  )) %>%
  # group_by(patientid) %>% 
  # mutate(first_treatment_date = case_when(
  #   str_detect(therapy, "Chemo")                      ~ min(episodedate),
  #   str_detect(therapy, "Surgery")                    ~ surgerydate,
  # )) %>% 
  # mutate(delay_incare_dx_to_treat = interval(start = diagnosisdate, end = first_treatment_date)/
  #                                         duration(n=1, units = "days")) %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  ungroup()

@@

```{r Table 3}
# tbl1 <- 
  analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           had_neo, had_adj,
           "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
#   filter(exclude != "1") %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>
